The CrypTool Script: \\ Cryptography, Mathematics and More \\ \vspace{30pt} {\large Background reading\\%*[-8pt] for the free e-learning program CrypTool\\ (10th edition -- distributed with CrypTool version 1.4.30)} \vspace{60pt}

### 2012-07-22 script/en/chapters/cryptomethods.tex
readme: minor update // script: update of overview, preface, introduction, appendices for function overviews of CT2 and JCT

% --------------------------------------------------------------------------
\section[Symmetric encryption]
{Symmetric encryption\footnotemark}
  \footnotetext{%
    With CrypTool\index{CrypTool} you can execute the following modern
    symmetric encryption algorithms 
    (using the menu path {\bf Crypt \textbackslash{} Symmetric (modern)}): \\
    IDEA, RC2, RC4, DES (ECB), DES (CBC), Triple-DES (ECB), Triple-DES (CBC),
    MARS (AES candidate), RC6 (AES candidate), Serpent (AES candidate), 
    Twofish (AES candidate), Rijndael (official AES algorithm).
    \index{AES}
  }
\nopagebreak
For {\em symmetric} encryption \index{Encryption!symmetric} sender and
recipient must be in possession of a common (secret) key which they have
exchanged before actually starting to communicate. The sender uses this
key to encrypt the message and the recipient uses it to decrypt it.
\par \vskip + 3pt

@@

More details about the AES algorithms and the AES candidates of the last round
can be found within the online help of CrypTool\index{CrypTool}%
\footnote{%
      CrypTool online help\index{CrypTool}: The index head-word {\bf AES}
      leads to the 3 help pages: {\bf AES candidates}, 
      {\bf The AES winner Rijndael} and 
      {\bf The Rijndael encryption algorithm}.
  }.

>>>>

% --------------------------------------------------------------------------
\section[Symmetric encryption]
{Symmetric encryption\footnotemark}
  \footnotetext{%
    With {\bf CrypTool 1}\index{CrypTool 1} you can execute the following modern
    symmetric encryption algorithms 
    (using the menu path {\bf Crypt \textbackslash{} Symmetric (modern)}):\\
    IDEA, RC2, RC4, DES (ECB), DES (CBC), Triple-DES (ECB), Triple-DES (CBC),
    MARS (AES candidate), RC6 (AES candidate), Serpent (AES candidate), 
    Twofish (AES candidate), Rijndael (official AES algorithm)\index{AES}.

    With {\bf CrypTool 2}\index{CrypTool 2} you can execute the following modern
    symmetric encryption algorithms (using in the Startcenter Templates
    \textbackslash{} Cryptography \textbackslash{} Modern \textbackslash{}
    Symmetric):\\
    AES, DES, PRESENT, RC2, RC4, SDES, TEA, TripleDES, Twofish.

    In {\bf JCrypTool}\index{JCrypTool} you can execute the following modern
    symmetric encryption algorithms:\\ 
    AES, Rijndael, Camellia, DES, Dragon, IDEA, LFSR, MARS, Misty1, RC2, RC5,
    RC6, SAFER+, SAFER++, Serpent, Shacal, Shacal2, Twofish.
  }
\nopagebreak
For {\em symmetric} encryption \index{Encryption!symmetric} sender and
recipient must be in possession of a common (secret) key which they have
exchanged before actually starting to communicate. The sender uses this
key to encrypt the message and the recipient uses it to decrypt it.
\par \vskip + 3pt

@@

More details about the AES algorithms and the AES candidates of the last round
can be found within the online help of CrypTool\index{CrypTool}%
\footnote{%
      CrypTool 1 online help\index{CrypTool 1}: The index head-word {\bf AES}
      leads to the 3 help pages: {\bf AES candidates}, 
      {\bf The AES winner Rijndael} and 
      {\bf The Rijndael encryption algorithm}.
  }.

### 2012-07-22 script/en/chapters/introduction.tex
readme: minor update // script: update of overview, preface, introduction, appendices for function overviews of CT2 and JCT

% --------------------------------------------------------------------------
\clearpage\phantomsection
\addcontentsline{toc}{chapter}{Preface to the 10th Edition of the CrypTool Script}
\chapter*{Preface to the 10th Edition of the CrypTool Script}

@@

In order to also enable developers/authors to work together independently 
the topics have been split up and for each topic an extra chapter has been 
written which can be read on its own. The later editorial work in TeX added 
cross linkages between different sections and footnotes describing where you
can find the according functions within the CrypTool 1\index{CrypTool 1.x} 
program \hyperlink{appendix-menutree}{(see menu tree} in appendix \ref{s:appendix-menutree}).
% \hypertarget{appendix-menutree}{}\label{s:appendix-menutree}
Naturally there are many more interesting topics in mathematics and
cryptography which could be discussed in greater depth -- therefore this
is only one of many ways to do it.

@@

%This edition of the script adds some topics, but mainly updates areas (e.g. the
%summaries of topical research areas):
This edition completely updated the TeX sources of the document, and of course
the content of the script was corrected, amended and updated with some topics, e.g.:
\vspace{-5pt}
\begin{itemize}
  \item the largest prime numbers (chap. \ref{search_for_very_big_primes}),
        new factorization records (chap. \ref{RSA-768}),
  \item progress in cryptanalysis of AES 
        (chap. \ref{NeueAES-Analyse}) and
%  \item progress in cryptanalysis of hash algorithms 
%        (chap. \ref{collision-attacks-against-sha-1}) and
%  \item progress in ideas for new crypto methods (RSA successor) 
%        (chap. \ref{xxxxxxxxxBrute-force-gegen-Symmetr})\index{xxxxxxxxxxxxxxxx} and
  \item the list of movies or novels, in which cryptography or number theory 
        played major role (see appendix \ref{s:appendix-movies});
        and where primes are used as hangers  
        (see curiouses in \ref{HT-Quaint-curious-Primes-usage}).
  \item Newly added are e.g. the section about Benford's law and primes
        (chap. \ref{primes:Benford-Law}), and 
        the appendix \ref{s:appendix-using-sage} about using the
        computer algebra system Sage. Sage becomes
        more and more the standard open-source CAS system. Accordingly all
        samples written before in Pari-GP and Mathematica have been substituted
        with Sage code. Thanks to Nguyen and Massierer, a lot of new code
        samples could be added (see also chap.~\ref{ec:Sage_Massierer}).
\end{itemize}

The first time the document was delivered with CrypTool\index{CrypTool} 
was in version 1.2.01. Since then it has been expanded and revised in almost
every new version of CrypTool.

@@

I hope that many readers have fun with this script and that they get 
out of it more interest and greater understanding of this modern but 
also very ancient topic.
\\
\\
% [1.5\baselineskip]
% \enlargethispage*{2\baselineskip}
% \nopagebreak
Bernhard Esslinger
\\
\\
% [\baselineskip]
Frankfurt (Germany), January 2010

@@

This document is delivered together with the open-source program CrypTool 1\index{CrypTool}.

The articles in this script are largely self-contained and
can also be read independently of CrypTool\index{CrypTool}.

@@

CrypTool\index{CrypTool} is used world-wide for training in companies and
teaching at schools and universities worldwide, and
several universities are helping to further develop the project.
\par \vskip + 15pt

@@

At this point I'd like to thank explicitly the following people who
particularly contributed to CT1\index{CrypTool}. They applied their
very special talents and showed really great engagement:
\vspace{-7pt}
%\begin{itemize}
\begin{list}{\textbullet}{\addtolength{\itemsep}{-0.5\baselineskip}}
   \item Mr.\ Henrik Koy
   \item Mr.\ J\"org-Cornelius Schneider
   \item Mr.\ Florian Marchal
   \item Dr.\ Peer Wichmann
   \item Staff of Prof.\ Claudia Eckert, Prof.\ Johannes Buchmann,
         Prof.\ Torben Weis and Prof.\ Arno Wacker..
\end{list}
%\end{itemize}
Also I want to thank all the many people not mentioned here for their 
hard work (mostly carried out in their spare time).
\\
\\
Bernhard Esslinger
\\
\\
Frankfurt (Germany), July 2012

>>>>

% --------------------------------------------------------------------------
\clearpage\phantomsection
\addcontentsline{toc}{chapter}{Preface to the 11th Edition of the CrypTool Script}
\chapter*{Preface to the 11th Edition of the CrypTool Script}

@@

Topics from mathematics and cryptography have been meaningfully split up and
for each topic an extra chapter has been written which can be read on its own.
This enables developers/authors to contribute independently of each other.
Naturally there are many more interesting topics in cryptography which could
be discussed in greater depth -- therefore this selection is only one of many
possible ways.

The later editorial work in TeX added cross linkages between different sections and footnotes describing where you can find the according functions within
the CrypTool programs. The appendices \ref{s:appendix-menu-overview-CT1} etc. contain a complete overview
of\index{CrypTool 1.x}\index{CrypTool 2}\index{JCrypTool}
the \hyperlink{menu-overview-CT1}{CrypTool 1 menu tree},
the \hyperlink{template-overview-CT2}{CrypTool 2 templates} and
the \hyperlink{function-overview-JCT}{JavaCrypTool (JCT) functions}.

@@

This edition of the CT script again updated some topics:
%This edition completely updated the TeX sources of the document, and of course
%the content of the script was corrected, amended and updated with some topics, e.g.:
\vspace{-5pt}
\begin{itemize}
  \item the definitions of the strength of security functions
        (Kap. \ref{cm_Section_Security_Definitions}),
  \item the largest prime numbers (chap. \ref{search_for_very_big_primes}),
        new factorization records (chap. \ref{RSA-768}),
%  \item progress in cryptanalysis of AES 
%        (chap. \ref{NeueAES-Analyse}) and
%  \item progress in cryptanalysis of hash algorithms 
%        (chap. \ref{collision-attacks-against-sha-1}) and
%  \item progress in ideas for new crypto methods (RSA successor) 
%        (chap. \ref{xxxxxxxxxBrute-force-gegen-Symmetr})\index{xxxxxxxxxx} and
  \item the list of movies or novels, in which cryptography or number theory 
        played a major role (see appendix \ref{s:appendix-movies});
        and where primes are used as hangers  
        (see curiouses in \ref{HT-Quaint-curious-Primes-usage}).
  \item Newly added are the functions overviews 
        \hyperlink{template-overview-CT2}{for CT2} and
        \hyperlink{function-overview-JCT}{(for JCT},
        further Sage scripts for cryptography and the appendix
        \ref{s:appendix-using-sage} about using the computer algebra system
        Sage. Sage becomes more and more the standard open-source CAS system.
        % Nguyen and Massierer (see also chap.~\ref{ec:Sage_Massierer}).
\end{itemize}

The script was delivered the first time with CrypTool\index{CrypTool} in
version 1.2.01. Since then it has been expanded and revised in almost
every new version of CrypTool 1.

@@

I hope that many readers have fun with this script and that they get 
out of it more interest and greater understanding of this modern but 
also very ancient topic.
\\
\\
% [1.5\baselineskip]
% \enlargethispage*{2\baselineskip}
% \nopagebreak
Bernhard Esslinger
\\
\\
% [\baselineskip]
Frankfurt (Germany), July 2012

@@

This document is delivered together with the open-source program
CrypTool 1\index{CrypTool 1.x}.

The articles in this script are largely self-contained and
can also be read independently of the CrypTool programs.

@@

CrypTool 1\index{CrypTool 1.x} and the successor versions
CrypTool 2 (CT2)\index{CrypTool 2.0} and JCrypTool (JCT)\index{JCrypTool 1.0}
are used world-wide for training in companies and teaching at schools and
universities.
\par \vskip + 15pt

@@

At this point I'd like to thank explicitly the following people who
particularly contributed to CT1\index{CrypTool}. They applied their
very special talents and showed really great engagement:
\vspace{-7pt}
%\begin{itemize}
\begin{list}{\textbullet}{\addtolength{\itemsep}{-0.5\baselineskip}}
   \item Mr.\ Henrik Koy
   \item Mr.\ J\"org-Cornelius Schneider
   \item Mr.\ Florian Marchal
   \item Dr.\ Peer Wichmann
   \item Staff of Prof.\ Claudia Eckert, Prof.\ Johannes Buchmann,
         Prof.\ Torben Weis and Prof.\ Arno Wacker.
\end{list}
%\end{itemize}
Also I want to thank all the many people not mentioned here for their 
hard work (mostly carried out in their spare time).
\\
\\
Bernhard Esslinger
\\
\\
Frankfurt (Germany), July 2012

### 2012-07-22 script/en/chapters/menus.tex
readme: minor update // script: update of overview, preface, introduction, appendices for function overviews of CT2 and JCT

% ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
%\pagebreak
\newpage
\enlargethispage{1cm}
\hypertarget{appendix-menutree}{}
\section{CrypTool Menus}
\label{s:appendix-menutree}

This appendix contains at the following page the complete menu tree of
CrypTool\index{CrypTool} version 1.4.31\footnote{%
  In parallel to CrypTool 1.x (CT1)\index{CrypTool 1.x} the future versions
  CrypTool 2 (CT2)\index{CrypTool 2.0} and JCrypTool (JCT)\index{JCrypTool 1.0}
  are currently developed in the CrypTool project.\\
  - Webseite CT2: \url{http://www.cryptool2.vs.uni-due.de} \\
  - Webseite JCT: \url{http://jcryptool.sourceforge.net} \\
  These future versions are currently (July 2012) beta versions, but they
  are stable enough to be used by end-users already.\\
}.

\noindent The main menu of CT1 contains service functions in the menus
\begin{itemize}
   \item File
   \item Edit
   \item View
   \item Options
   \item Window
   \item Help
\end{itemize}
and the actual cyrpto functions in the menus
\begin{itemize}
   \item Encrypt/Decrypt
   \item Digital Signature/PKI
   \item Individual Procedures
   \item Analysis.
\end{itemize}

Below \verb#Individual Procedures# you find visualizations of single algorithms
and of protocols. Some procedures are implemented both for a fast performance
(mostly under the main menu \verb#Encrypt/Decrypt#) and for a step-by-step visualization.

Which menu items in CrypTool are active (that means not greyed), depends on
the type of the currently active document window:
The brute-force analysis\index{Attack!brute-force} for DES e.~g. is only
available, if the active window is opened in the hexadecimal view. 
On the other hand the menu item ``Generate Random Numbers\dots''
is always available (even if no document is opened).

@@

%\nobreak
\clearpage
\begin{figure}[hb]
\begin{center}
\vspace{-30pt}
%\frame{  %TeX macht einen Rahmen (siehe viewport) drumherum -- gut zum Testen
%\includegraphics[scale=0.25, angle=270, viewport=200 30 2660 1430]
\includegraphics[scale=0.35, angle=270]
                {figures/CT1-menutree-en}
%viewport=rand-links? rand-unten breite hoehe? [bezogen auf querformat]
%}
\caption{Complete overview of the menu tree of CT1 (CrypTool 1.4.31)} 
\label{menuoverview}
\end{center}
\end{figure}
\clearpage

\noindent Text for CT2 xxxxxxxxxx DRAFT

\clearpage
\begin{figure}[hb]
\begin{center}
\vspace{-30pt}
\includegraphics[scale=0.8, angle=270]
                {figures/CT2-templatetree-en}
\caption{Overview of the template tree of CT2 (NB4882.1, July 2012), Part 1} 
\label{menuoverview}
\end{center}
\end{figure}
\clearpage

>>>>

% ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
%\pagebreak
\newpage
%\enlargethispage{1cm}
\hypertarget{appendix-menu-overview-CT1}{}
\section{CrypTool 1 Menus}
\label{s:appendix-menu-overview-CT1}

This appendix contains at the following page the complete menu tree of
CrypTool\index{CrypTool} version 1.4.31\footnote{%
  Since 2010, changes for the stable CrypTool 1.x (CT1)\index{CrypTool 1.x}
  focus mainly on bugfixes. All new developments go into the two successor
  versions CrypTool 2 (CT2)\index{CrypTool 2.0} and
  JCrypTool (JCT)\index{JCrypTool}:\\
  - Web site CT2: \url{http://www.cryptool.org/en/ct2-documentation-en} \\
  - Web site JCT: \url{http://www.cryptool.org/en/jct-volunteer-en} \\
  These successor versions are currently (July 2012) still beta versions;
  but they are close to their first release and they are already stable
  enough to be used by end-users.\\
}.

\noindent The main menu of CT1 contains both, generic service functions in the
six main menu items
\begin{itemize}
   \item File
   \item Edit
   \item View
   \item Options
   \item Window
   \item Help,
\end{itemize}
and the actual crypto functions in the following four main menus
\begin{itemize}
   \item Encrypt / Decrypt
   \item Digital Signature / PKI
   \item Individual Procedures
   \item Analysis.
\end{itemize}

Within \verb#Individual Procedures# you find visualizations of single algorithms
and of protocols. Some procedures are implemented both for a fast performance
(mostly under the main menu \verb#Encrypt/Decrypt#) and for a step-by-step visualization.

Which of the menu items in CrypTool 1 are active (that means not greyed),
depends on the type of the currently active document window:
The brute-force analysis\index{Attack!brute-force} for DES e.~g. is only
available, if the active window is opened in the hexadecimal view. 
On the other hand the menu item ``Generate Random Numbers\dots''
is always available (even if no document is opened).

@@

%\nobreak
\clearpage
\begin{figure}[hb]
\begin{center}
\vspace{-30pt}
%\frame{  %TeX macht einen Rahmen (siehe viewport) drumherum -- gut zum Testen
%\includegraphics[scale=0.25, angle=270, viewport=200 30 2660 1430]
\includegraphics[scale=0.35, angle=270]
                {figures/CT1-menutree-en}
%viewport=rand-links? rand-unten breite hoehe? [bezogen auf querformat]
%}
\hypertarget{menu-overview-CT1}{}
\caption{Complete overview of the menu tree of CT1 (CrypTool 1.4.31)} 
\label{menu-overview-CT1}
\end{center}
\end{figure}
\clearpage

\newpage
%\enlargethispage{1cm}
\hypertarget{appendix-template-overview-CT2}{}
\section{CrypTool 2 Templates}
\label{s:appendix-template-overview-CT2}

\noindent This appendix contains on the following pages the complete tree with
all templates in CT2\index{CrypTool 2}.\footnote{%
  You can find further information about CT2 at:
  \url{http://www.cryptool.org/en/ct2-documentation-en}
}

\noindent When you start CT2 it first shows the Startcenter.

%\clearpage
\begin{figure}[hb]
\begin{center}
%\vspace{-30pt}
\includegraphics[scale=0.45, angle=0] {figures/CT2-Startcenter-en}
\hypertarget{Welcome-CT2}{}
\caption{Startcenter in CT2 (Beta 8b, May 2012)} 
\label{Welcome-Screenshot-CT2}
\end{center}
\end{figure}
%\clearpage

\noindent Within the Startcenter you have three main ways to use the implemented functionality:
\begin{itemize}
   \item the Wizard, which leads you to the functions.
   \item the Workspace, where you can compose the components by yourself according to the visual programming\index{Visual programming} concept.
   \item the template tree, which offers ready-to-run workflows.
 \end{itemize}

The Wizard asks questions so you can get to the desired scenarios (e.g. base64 coding) and then runs the according functions. You can afterwards save the chosen scenario as a normal template including the entries you used.

The empty workspace allows to drag on it any component from the navigation bar on the left and connect these components in the way you like. Most of the crypto functionality implemented in CT2 is offered using these components (e.g. Enigma, AES).

The template tree contains at least one template for each implemented component. The offered templates contain read-to-run workflows. If you change e.g. within the AES template your input, you can see at once, how the output is modified dynamically (e.g. adding another block via padding, influence of the chosen chaining, ...).

\clearpage
\begin{figure}[hb]
\begin{center}
\vspace{-30pt}
\includegraphics[scale=0.8, angle=270]
                {figures/CT2-templatetree-en-1}
\hypertarget{template-overview-CT2}{}
\caption{Screenshot of the template tree of CT2 (NB4882.1, July 2012), Part 1} 
\label{template-overview-CT2}
\end{center}
\end{figure}
\clearpage

\newpage
%\enlargethispage{1cm}
\hypertarget{appendix-function-overview-JCT}{}
\section{JCrypTool Functions}
\label{s:appendix-function-overview-JCT}

\noindent On the following pages this appendix contains a list of all
functions in JCrypTool\index{JCrypTool}.\footnote{%
  You can find further information about JCT at:
  \url{http://www.cryptool.org/en/jct-volunteer-en} \\
  This list was generated using the CT Portal website.}

\noindent When you start JCT the first time it shows the Welcome window.

%\clearpage
\begin{figure}[hb]
\begin{center}
%\vspace{-30pt}
\includegraphics[scale=0.45, angle=0] {figures/JCT-Welcome-EN}
\hypertarget{welcome-JCT}{}
\caption{Welcome screenshot in JCT (RC6, July 2012)} 
\label{Welcome-Screenshot-JCT}
\end{center}
\end{figure}
%\clearpage
After pressing ``Start'' you can directly use the different functions.
The functions implemented in JCT are presented in two different perspectives:
\begin{itemize}
   \item Default Perspective
   \item Funktional Perspective
 \end{itemize}

All functions of the {\bf Default Perspective} can be found both in the menus and in the navigation bar called ``Crypto Explorer'' (at the right side).
The Default Perspective contains all important methods like classic transposition or modern AES, and many visualizations (e.g. Diffie-Hellman key exchange or caculations on elliptic curves).

All functions of the {\bf Functional Perspective} can be found in the navigation bar called ``Algorithms'' (in this perspective also at the right side).
The Functional Perspective contains all detail settings of the various algorithms, it especially offers post-quantum computing algorithmss\index{Post-quantum computing}.

\clearpage
\begin{figure}[hb]
\begin{center}
\vspace{-30pt}
\includegraphics[scale=0.8, angle=0] {figures/JCT-functions-en-1}
\hypertarget{template-overview-CT2}{}
\caption{Screenshot of the functions of JCT (RC6, July 2012), Part 1} 
\label{functions-overview-1-JCT}
\end{center}
\end{figure}
\clearpage

\clearpage
\begin{figure}[hb]
\begin{center}
\vspace{-30pt}
\includegraphics[scale=0.8, angle=0] {figures/JCT-functions-en-2}
\hypertarget{template-overview-CT2}{}
\caption{Screenshot of the functions of JCT (RC6, July 2012), Part 2} 
\label{functions-overview-2-JCT}
\end{center}
\end{figure}
\clearpage

### 2012-07-22 script/en/script-en.tex
CT Script: Added chap 1.1 (sec def), and added OTP in 2.2.4 (EN only yet)
CT script: Finished de translation of chap 1.1; added draft covers de and en)
readme: minor update // script: update of overview, preface, introduction, appendices for function overviews of CT2 and JCT

% Hier wird \vspace{32pt} einfach ignoriert
\author{ % Die Klammer zur Fontänderung funktioniert bei author nur einzeilig im Gegensatz zu title?!
        {\LARGE Copyright (c) Prof.\ Bernhard Esslinger (co-author and editor)}\\[5pt]
        {\LARGE and the CrypTool Development Team, 1998-2012}\\[5pt]
        {\LARGE Frankfurt am Main, Germany xxx} \\*[15pt]
        \url{www.cryptool.org}
}

@@

% \includepdf[page=1]{figures/coverv1_en-300dpi.pdf}
\includepdf[page=1]{figures/coverv1_en.pdf}

@@

% ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\begin{appendix}
\newpage
\hypertarget{appendix-start}{}\label{s:appendix-start}
\chapter{Appendix}
    \begin{itemize}
      \item[1] \hyperlink{appendix-menutree}{CrypTool Menu Tree}
      \item[2] \hyperlink{appendix-authors}{Authors of the CrypTool Script}
      \item[3] \hyperlink{appendix-authors}{Bibliography of Movies and
                     Fictional Literature with Relation to Cryptography,
                     Books for Kids with Collections of Simple Ciphers}
      \item[4] \hyperlink{appendix-Learn-NT}
                     {Learning Tool for Elementary Number Theory}
      \item[5] \hyperlink{appendix-using-sage}
                     {Using Sage with this Script}
    \end{itemize}
  \newpage
  \input{chapters/menus.tex}
  \input{chapters/authors.tex}
  \input{chapters/what-is-sage.tex}
\end{appendix}

>>>>

% Hier wird \vspace{32pt} einfach ignoriert
\author{ % Die Klammer zur Fontänderung funktioniert bei author nur einzeilig im Gegensatz zu title?!
        {\LARGE Copyright (c) Prof.\ Bernhard Esslinger (co-author and editor)}\\[5pt]
        {\LARGE and the CrypTool Development Team, 1998-2012}\\[5pt]
        {\LARGE Frankfurt am Main, Germany} \\*[15pt]
        \url{www.cryptool.org}
}

@@

% \includepdf[page=1]{figures/coverv1_en-300dpi.pdf}
% \includepdf[page=1]{figures/coverv1_en.pdf}
\includepdf[page=1]{figures/coverv1_en_draft.pdf}

@@

% ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\begin{appendix}
\newpage
\hypertarget{appendix-start}{}\label{s:appendix-start}
\chapter{Appendix}
    \begin{itemize}
      \item[1] \hyperlink{appendix-menu-overview-CT1}{CrypTool 1 Menu Tree}
      \item[2] \hyperlink{appendix-template-overview-CT2}{CrypTool 2 Templates}
      \item[3] \hyperlink{appendix-function-overview-JCT}{JCrypTool Functions}
      \item[4] \hyperlink{appendix-authors}{Bibliography of Movies and
                     Fictional Literature with Relation to Cryptography,
                     Books for Kids with Collections of Simple Ciphers}
      \item[5] \hyperlink{appendix-Learn-NT}
                     {Learning Tool for Elementary Number Theory}
      \item[6] \hyperlink{appendix-using-sage}
                     {Using Sage with this Script}
      \item[7] \hyperlink{appendix-authors}{Authors of the CrypTool Script}
    \end{itemize}
  \newpage
  \input{chapters/menus.tex}
  \input{chapters/movies.tex}
  \input{chapters/what-is-sage.tex}
  \input{chapters/authors.tex}
\end{appendix}
